The ChEMBL database as Linked Open Data

### 2012-04-15 article.tex
change rdfs:seeAlso for pubmed to skos:exactMatch
Checked state, and updated internal notes
More complete addresses

\address[A]{Department of Bioinformatics - BiGCaT, Maastricht University, ADDRESS, Maastricht,\\ The Netherlands}
\address[B]{Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden}
\address[C]{University of Queensland, St Lucia, Qld 4072, Australia}
\address[D]{Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A.}
\address[E]{ChEBI, European Bioinformatics Institute}
\address[F]{ChEMBL, European Bioinformatics Institute}
\address[G]{Indiana University}

@@

\begin{tiny}
\begin{verbatim}
res:r23 rdfs:seeAlso <http://bio2rdf.org/pubmed:15149661> .
\end{verbatim}
\end{tiny}

@@

%Peter: write up the proxying... if that still works... It was broken through disuse, but is available again in its rdf.farmbio.uu.se configuration, separately from the bio2rdf-webapp at https://github.com/ansell/chembl-webapp/

>>>>

\address[A]{Department of Bioinformatics - BiGCaT, Maastricht University, P.O. Box 616, UNS50 Box 19, NL-6200 MD, Maastricht, The Netherlands}
\address[B]{Department of Pharmaceutical Biosciences, Uppsala University, PO Box 591, SE-751 24, Uppsala, Sweden}
\address[C]{University of Queensland, St Lucia, Qld 4072, Australia}
\address[D]{Royal Society of Chemistry, 904 Tamaras Circle, Wake Forest, NC 27587, U.S.A.}
\address[E]{Chemoinformatics and Metabolism, European Bioinformatics Institute, POSTAL CODE, Hinxton, United Kingdom}
\address[F]{EMBL-European Bioinformatics Institute, Wellcome Trust Genome Campus, Hinxton, Cambridgeshire, CB10 1SD, United Kingdom}
\address[G]{School of Informatics and Computing, Indiana University, Bloomington, IN, U.S.A.}

@@

\begin{tiny}
\begin{verbatim}
res:r23 skos:exactMatch <http://bio2rdf.org/pubmed:15149661> .
\end{verbatim}
\end{tiny}

@@
